\section{Development tools}
\subsection{Efficient looping (\texttt{itertools})}
Infinite iterators:
\begin{compactenum}
\item \mintinline{python}{count}: evenly spaced values: $a$, $a+ r$, \ldots
\item \mintinline{python}{cycle}: turns iterable into infinite sequence.
\item \mintinline{python}{repeat}: repeats an object indefinitely, unless second argument (\emph{times}) is specified.
\end{compactenum}

Iterators terminating on the shortest input sequence:
\begin{compactenum}
\item \mintinline{python}{accumulate}: accumulates binary function (sum)
\item \mintinline{python}{chain}: consecutive sequences as a single one.
\item \mintinline{python}{compress}: an iterator that filters elements from \emph{data} having a corresponding element in \emph{selectors} that evaluates to True.
\item \mintinline{python}{dropwhile}: drops elements from the iterable as long as the predicate is true.
\item \mintinline{python}{filterfalse}: filters elements to those for which the predicate is false.
\item \mintinline{python}{groupby}: \emph{\color{red} missing description}
\item \mintinline{python}{islice}: \emph{\color{red} missing description}
\item \mintinline{python}{starmap}: iterator computing a function using arguments obtained from iterable.
\item \mintinline{python}{takewhile}: takes elements from the iterable as long as the predicate is true.
\item \mintinline{python}{tee}: $n$ intependent iterators from one.
\item \mintinline{python}{zip_longest}: like regular \mintinline{python}{zip}, but fills missing values instead of truncating.
\end{compactenum}

Combinatoric generators:
\begin{compactenum}
\item \mintinline{python}{product}: cartesian product of iterables.
\item \mintinline{python}{permutations}: $r$-length tuples, all possible orderings, no repeated elements.
\item \mintinline{python}{combinations}: sorted permutations.
\item \mintinline{python}{combinations_with_replacement}: $r$-length sorted tuples, with repetitions.
\end{compactenum}

\subsection{Higher order functions (\texttt{functools})}

\subsection{Operators as functions (\texttt{operator})}
