\section{Built-in types}
\subsection{Booleans}
There are three Boolean operations: \mintinline{python}{or}, \mintinline{python}{and} and \mintinline{python}{not}.
There are eight comparison operations, which can be chained and have higher priority than the Boolean operations:
\mintinline{python}{<}, 
\mintinline{python}{<=}, 
\mintinline{python}{>}, 
\mintinline{python}{>=}, 
\mintinline{python}{==}, 
\mintinline{python}{!=}, 
\mintinline{python}{is}, 
\mintinline{python}{is not}.

\subsection{Numeric types}
Python supports three numeric types: integers, floats and complex numbers.
Integers have unlimited precision.
Complex numbers have real (\mintinline{python}{z.real}) and imaginary part (\mintinline{python}{z.imag}),
both are floats.

Numeric types support the following operations, sorted by ascending priority:
\begin{compactenum}
\item \mintinline{python}{+}, \mintinline{python}{-}, \mintinline{python}{*}, \mintinline{python}{/}, 
\item \mintinline{python}{//} (floored quotient), \mintinline{python}{%} (remainder),
\item \mintinline{python}{abs(x)},
\item \mintinline{python}{int(x)}, \mintinline{python}{float(x)}, \mintinline{python}{complex(re, im)},
\item \mintinline{python}{c.conjugate}, 
\item \mintinline{python}{divmod} (quotient and remanider),
\item \mintinline{python}{pow(x, y) == x**y}.
\end{compactenum}

Bitwise operations, \mintinline{python}{|} (or), \mintinline{python}{^} (xor), \mintinline{python}{&} (and), \mintinline{python}{<<}, \mintinline{python}{>>} (shifts) and \mintinline{python}{~} (inversion) only make sense for integers.

\subsection{Iterator types}
To-do.

\subsection{Sequence types}
There are three basic sequence types: 
lists, tuples, and range objects. 
Common sequence operations include:
\begin{compactenum}
\item \mintinline{python}{x in s} and \mintinline{python}{x not in s},
\item \mintinline{python}{s + t}, the concatenation,
\item \mintinline{python}{s * n}, adding \texttt{s} to itself \texttt{n} times,
\item \mintinline{python}{s[i]}, $i$th item of \texttt{s} and \mintinline{python}{s[i:j:k]}, slicing,
\item \mintinline{python}{len(s)}, \mintinline{python}{min(s)}, \mintinline{python}{max(s)},
\item \mintinline{python}{s.index(x)}, index of the first occurrence,
\item \mintinline{python}{s.count(x)}, total number of occurrences.
\end{compactenum}

Mutable sequence types support following operations:
\begin{compactenum}
\item \mintinline{python}{del s[i:j:k]} removes the elements,
\item \mintinline{python}{s.append(x)}, 
\item \mintinline{python}{s.clear()} removes all elements,
\item \mintinline{python}{s.copy()} creates a shallow copy, 
\item \mintinline{python}{s.extend(t)},  
\item \mintinline{python}{s *= n},  
\item \mintinline{python}{s.insert(i, x)},  
\item \mintinline{python}{s.pop([i])} removes an item, retrieves it,  
\item \mintinline{python}{s.remove(x)},  
\item \mintinline{python}{s.reverse()} reverses the items in place.  
\end{compactenum}

Lists are mutable and typically store collections of homogeneous items.
They provide the method \mintinline{python}{sort}, which sorts the list in place.
May be constructed using:
\begin{compactenum}
\item a pair of square brackets: \mintinline{python}{[]}, \mintinline{python}{[1, 2, 3]},
\item a comprehension: \mintinline{python}{[x for x in iter]}, 
\item the type constructor: \mintinline{python}{list(iter)}.
\end{compactenum}

Tuples are immutable and typically store collections of heterogeneous data.
May be constructed using:
\begin{compactenum}
\item a pair of parantheses: \mintinline{python}{()}, \mintinline{python}{(1,)},
\item the \mintinline{python}{tuple(iterable)} built-in.
\end{compactenum}

Ranges are immutable sequence of numbers.
May be constructed using: \mintinline{python}{range(stop)} or the longer version, \mintinline{python}{range(start, stop, step)}.

Useful:
\begin{minted}{python}
for index, value in enumerate(list):
    commands
\end{minted}




\subsection{Text sequence type}
Strings are immutable sequences of Unicode code points surrounded by single, double or triple quotes.

\begin{compactenum}
\item Case conversion:
\begin{compactenum}
\item \mintinline{python}{.capitalize()},
\item \mintinline{python}{.casefold()} (aggresive lowercase),
\item \mintinline{python}{.lower(), lstrip()},
\item \mintinline{python}{.swapcase()},
\item \mintinline{python}{.title()},
\item \mintinline{python}{.upper()}.
\end{compactenum}
\item Justification:
\begin{compactenum}
\item \mintinline{python}{.center(width, fillchair)},
\item \mintinline{python}{.ljust(width, fillchair)},
\item \mintinline{python}{.rjust(width, fillchar)},
\item \mintinline{python}{.zfill()} left fills with zeroes.
\end{compactenum}
\item Search and/or replace:
\begin{compactenum}
\item \mintinline{python}{.count(sub, start, end)},
\item \mintinline{python}{.find(sub, start, end)},
\item \mintinline{python}{.rfind(sub, start, end)},
\item \mintinline{python}{.index(sub)} like \mintinline{python}{find}, raises error when text is not found (not $-1$),
\item \mintinline{python}{.rindex(sub, start, end)},
\item \mintinline{python}{.replace(old, new, count)},
\item \mintinline{python}{.endswith(suffix)},
\item \mintinline{python}{.startswith(prefix)},
\end{compactenum}
\item Joining and splitting:
\begin{compactenum}
\item \mintinline{python}{.join(iterable)},
\item \mintinline{python}{.partition(sep)} returns 3-tuple,
\item \mintinline{python}{.rpartition(sep)} from right,
\item \mintinline{python}{.split()} splits into the same type,
\item \mintinline{python}{.rsplit()} splits from right,
\item \mintinline{python}{.splitlines()},
\end{compactenum}
\item \mintinline{python}{.format(*args, **kwargs)},
\item \mintinline{python}{.strip()} removes leading/trailing chars,
\item \mintinline{python}{.rstrip()} removes trailing chars only.
\end{compactenum}

% \subsection{Binary sequence types}

\subsection{Set types}
A set object is an unordered collection of distinct hashable objects.
The \mintinline{python}{set} is mutable, \mintinline{python}{frozenset} is not.
Sets support following operations:
\begin{compactenum}
	\item \mintinline{python}{len(s)}, \mintinline{python}{x in s}, \mintinline{python}{x not in s},
	\item \mintinline{python}{copy()}: returns a shallow copy,
	\item \mintinline{python}{.isdisjoint(other)},
	\item \mintinline{python}{.issubset(other)}: \mintinline{python}{set1 <= set2},
	\item \mintinline{python}{.issuperset(other)}: \mintinline{python}{set1 >= set2},
	\item \mintinline{python}{set1 < set2}: being proper subset,
	\item \mintinline{python}{set1 > set2}: being proper superset,
	\item \mintinline{python}{union(*sets)}: \mintinline{python}{set1 | set2 | ...},
	\item \mintinline{python}{intersection(*sets)}: \mintinline{python}{set1 & set2 ...}, 
	\item \mintinline{python}{difference(*sets)}: \mintinline{python}{set1 - set2 - ...}, 
	\item \mintinline{python}{symmetric_difference(other)}: \mintinline{python}{set1 ^ set2}.
\end{compactenum}

Mutable sets support following operations as well:
\begin{compactenum}
	\item \mintinline{python}{.add()},
	\item \mintinline{python}{.remove()} raises errors,
	\item \mintinline{python}{.discard()} doesn't raise errors,
	\item \mintinline{python}{.pop()} removes and returns an element,
	\item \mintinline{python}{.clear()} removes all elements.
\end{compactenum}


\subsection{Mapping types (\texttt{dict})}
A (mutable) dictionary maps hashable values to arbitrary objects.

These are the operations that dictionaries support:
\begin{compactenum}
\item  \mintinline{python}{len(d)},
\mintinline{python}{d[key]},
\mintinline{python}{key in d},
\mintinline{python}{key not in d},
\item  \mintinline{python}{del d[key]} removes \texttt{d[key]} from \texttt{d}.
\item  \mintinline{python}{iter(d)} returns an iterator over keys,
\item  \mintinline{python}{clear()} removes all items,
\item  \mintinline{python}{copy()} returns a shallow copy,
\item \mintinline{python}{pop(key)}, \mintinline{python}{popitem()}, 
\item \mintinline{python}{items()} returns keys and values,
\item \mintinline{python}{keys()} returns keys,
\item \mintinline{python}{values}, 
\item \mintinline{python}{update()}.
\end{compactenum}




