\documentclass[a4paper, twoside, 8pt]{extarticle}
\usepackage[
    left=1.2cm,
    right=1.2cm,
    top=2.25cm,
    bottom=1.25cm]{geometry}
\usepackage{multicol}
\usepackage{textcomp}

\usepackage{fancyhdr} % extensive control of page headers and footers
\makeatletter
\fancypagestyle{mypagestyle}
{\newpage \fancyfoot[C]{} \renewcommand{\footrulewidth}{0pt}}
\makeatother
\pagestyle{mypagestyle}
\headsep 5pt            

\usepackage{minted} % highlighted source code
\usepackage[usenames,dvipsnames]{color} % colour control
\usepackage{xcolor} % driver-independent color extensions
\usepackage{amssymb} % provides an extended symbol collection

\usepackage{enumitem} % control layout of itemize, enumerate, description
\newenvironment{enumx} {
	\begin{enumerate}[leftmargin=*]
	\setlength{\topsep}{0pt}
	\setlength{\itemsep}{0pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	}
{\end{enumerate}}
\newenvironment{itemx} {
	\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
	%\setlength{\itemsep}{0pt}
	%\setlength{\parskip}{0pt}
	%$\setlength{\parsep}{0pt}
	}
{\end{itemize}}

\usepackage{parskip} % layout with zero \parindent, non-zero \parskip
\usepackage{titlesec} % selects alternative section titles
\titlespacing\section{0pt}{6pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{6pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{6pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\usepackage{lastpage} % reference last page
\usepackage{Alegreya}
\usepackage{hyperref}

\newcommand{\manualbreak}{\vspace*{\fill}\columnbreak}
\newcommand{\cmdblack}{$\blacksquare$}
\newcommand{\cmd}{$\bigstar$}
\newcommand{\python}[1] {\textbf{\color{blue}#1}}
 
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\begin{document}
\renewcommand{\footrulewidth}{0.4pt}
\fancyhead[LE,LO]{Python 3 -- cheat sheet (page \thepage/\pageref{LastPage})}
\fancyhead[RO,RE]{source: --} 
\fancyfoot[RF]{author: Remigiusz Suwalski, date: \today}
%\fancyfoot[LF]{}


\begin{multicols*}{3}
\raggedright
\section{Built-in types}

\subsection{Booleans}

\subsection{Numeric types}

% Iterator types

\subsection{Sequence types}

\subsection{Strings}
\begin{enumx}
\item Case conversion: 
\begin{itemx}
    \item \python{s.capitalize()} - Make every word start with a capitalized letter.
    \item \python{s.title()} - Make the first word capitalized.
    \item \python{s.casefold()} Make every word lowercase, aggressively.
          \python{s.lower()} Make every word lowercase.
          \python{s.upper()} Make every word uppercase.
      \item \python{s.swapcase()} Makes all uppercase letters lowercase, and vice versa.
\end{itemx}

\item Justification: 
\begin{itemx}
    \item \python{s.center(width)} Justifies \python{s} with spaces on each line, centering them.
    \item \python{s.ljust(length)} Makes \python{s} the specified width by inserting spaces on the left.
    \item \python{s.rjust(length)} Makes \python{s} the specified width by inserting spaces on the right.
    \item \python{s.zfill(length)} Makes \python{s} the specified width by inserting zeros (\python{'0'}) on the left of the string.

	\item \python{s.strip} Removes leading and trailing spaces.
\end{itemx}

\item Checks:
\begin{itemx}
    \item \python{s.startwith(x)} Checks if \python{s} starts with \python{x}.
    \item \python{s.endswith(x)} Checks if \python{s} ends with \python{x}.
    \item \python{x in s} Checks if \python{x} is contained within \python{s}.
\end{itemx}


\item Searching:
\begin{itemx}
\item \python{s.count(x)} Gives how man times \python{x} occurs in \python{s}.
\item \python{s.find(x)}, \python{s.index(x)} Gives the first index of \python{x} in \python{s}.
\end{itemx}

\item Splitting and joining:
\begin{itemx}
    \item \python{s.join(x)} Makes the list \python{x} into a string by inserting \python{s} in between every element of \python{x}.
    \item \python{s.split(x)} Separates \python{s} into a list by removing every occurrence of \python{x} and collecting everything in between into a list.
    \item \python{s.partition(x)} Like \python{s.split(x)}, but doesn't remove every occurrence of \python{x}.
\end{itemx}

\item Encoding: 
\begin{itemx}
    \item \python{s.encode(encoding='utf-8')} Encodes a string into a specified encoding (utf-8, etc.)
\end{itemx}
\end{enumx}

\subsection{Sets}

\subsection{Dictionaries}

\end{multicols*}
\end{document}