\section{Programming in Bash}
\subsection{Shebang}
The shebang (\texttt{\#!}) at the head of a script indicates an
interpreter for execution, as in \texttt{\#!/bin/bash}.
Lines starting with a \texttt{\#} (with the exception of shebang)
are comments and thus won't be executed.

\subsection{Quoting and literals}
\textbf{Single quotes} \texttt{''} preserve the literal value of characters enclosed within them.
A single quote may not appear between single quotes, even when escaped, but may appear between \textbf{double quotes} \texttt{""}.

They work similarly, with an exception that the shell expands any variables that appear within them.

\subsection{Variables}
\textbf{Variable} names are case sensitive.
They can contain digits and underscores as well,
but a name starting with a digit is not allowed.
Example:
\begin{minted}{bash}
var="kind"
echo ${var}ness # kindness
\end{minted}

Special variables:
\begin{compactenum}
    \item \texttt{\$0}: name of the script itself.
    \item \texttt{\$1}, \texttt{\$2}, \texttt{\$3}, \ldots: the first, second, etc. argument. \texttt{shift} removes first argument and advances rest of them forward.
    \item \texttt{\$*} and \texttt{\$@} denote all the positional parameters.
    \item \texttt{\$\#}: the number of positional parameters
    \item \texttt{\$?}: exit status of last executed command.
    \item \texttt{\$\$}: the process ID of the shell.
    \item \texttt{\$!}: the process ID of last executed command.
\end{compactenum}

To read a line of input, use \texttt{read} shell built-in.
\begin{compactenum}
\item [\cmdvar] \textbf{read} reads a line from the stdin: % and splits it into fields:
\item [\texttt{n}] returns after reading $n$ characters,
\item [\texttt{n}] displays a prompt.
\end{compactenum}

\subsection{Expansions}
''After the command has been split into tokens, these tokens or words are expanded or resolved. There are eight kinds of expansion performed, which we will discuss in the next sections, in the order that they are expanded.''

\subsubsection{Brace expansion}
Brace expansion is used when we need to generate all possible string combinations.
Both of the commands produce the same output:
\begin{minted}{bash}
echo {I,really,love,dots}.
echo I. really. love. dots.
\end{minted}

\textbf{Warning}: it does not expand the variables (\texttt{\$var}), which is done later, but supports ranges (sequences) of characters:
\begin{minted}{bash}
echo {a..t}
a b c d e f g h i j k l m n o p q r s t
\end{minted}

and (maybe zero paded or with an increment rate) integers, assuming the Bash version is 4 or newer:

\begin{minted}{bash}
echo {01..10..1}.~
01. 02. 03. 04. 05. 06. 07. 08. 09. 10.
\end{minted}

There is a tilde expansion as well.
The expressions \texttt{$\sim$} and \texttt{$\sim$<user>} expand to the home directory of the current (or given) user.

\vfill\null
\columnbreak

\subsubsection{Parameter expansion}
\begin{enumerate}
\item \mintinline{bash}{${var^}}, \mintinline{bash}{${var,}} convert first character to upper and lowercase. \mintinline{bash}{${var^^}}, \mintinline{bash}{${var,,}} do the same to all characters.

\mintinline{bash}{${var~}}, \mintinline{bash}{${var~~}} are undocumented now: they reverse the case.

In case of the array expansion, every expanded element changes case, no matter what.

\item \mintinline{bash}{${var#pattern}} removes the \texttt{pattern} from the beginning of the string, if possible.

It's greedy variant is \mintinline{bash}{${var##pattern}}.

\mintinline{bash}{${var%pattern}} and \mintinline{bash}{${var%%pattern}} do the same, but  from the end of the string.

Application: extracting parts of a filename.

\item \mintinline{bash}{${var/pattern/string}} performs a single search and replace operation.

\mintinline{bash}{${var//pattern/string}} searches for all occurrences of the pattern and replaces them.

\item \mintinline{bash}{${#var}} returns length of the string.

\item \mintinline{bash}{${var:offset:length}} skips first \texttt{offset} characters from \texttt{var} and truncates the output to given length.
\texttt{:length} may be skipped.

Negative values separated with extra space are accepted.

\item \mintinline{bash}{${var:-value}} uses a default value, if \texttt{var} is empty or unset.

\mintinline{bash}{${var:=value}} does the same, but performs an assignment as well.

\mintinline{bash}{${var:+value}} uses an alternative value if \texttt{var} isn't empty or unset!
\end{enumerate}

\subsubsection{Command substitution}
To execute commands in a subshell and then pass their standard output, use \mintinline{bash}{$( commands )}.

\subsubsection{Arithmetic expansion}
The arithmetic expression \mintinline{bash}{$(( ... ))} is evaluated and expands to the result.
Bash guarantees that the output will be a one-word integer.

\subsubsection{Process substitution}
This kind of substitution: \mintinline{bash}{<( ... )} and \mintinline{bash}{>( ... )} (not specified by POSIX!), where input or output of a command appears as a temporary file, is performed simultaneously with the following: arithmetic and parameter expansions, command substitution.


\subsection{Streams}
There are always three default files open:
\begin{compactenum}
\item \emph{stdin} (the keyboard, file descriptor 0),
\item \emph{stdout} (the screen, file descriptor 1) and
\item \emph{stderr} (error messages output, file descriptor 2).
\end{compactenum}

These \textbf{streams} can be \textbf{redirected}:
\begin{compactenum}
\item \texttt{cmd > file} redirects to a file (overwrites),
\item \texttt{cmd >{}> file} appends instead,
\item \texttt{m>n} (or \texttt{m>\&n}) redirects a file descriptor to a file
(or another file descriptor),
\item \texttt{\&>file} redirects stdout and stderr to a file,
\item \texttt{:> file} truncates file to zero length,
\item \texttt{|} (pipe) serves as a command chaining tool.
\end{compactenum}

Here document is a section of a source code file that is treated as if it were a separate file:

\begin{minted}{bash}
cat <<EOF > /path/to/your/file
   This line will write to the file.
EOF
\end{minted}

%\vfill\null
%\columnbreak

\subsection{Control flow statements}
The one-line constructs \texttt{\&\&} and \texttt{||} work not like and, or ($\wedge$, $\vee$), but the \emph{if -- then -- else} statement.

\subsubsection{Conditionals}
Here at least one statement must be specified inside every block,
but one can use a single colon (:) as a null statement to avoid
rewriting the code.

\begin{minted}{bash}
if condition; then
  commands
elif second_condition; then
  some_commands
else
  other_commands	
fi

select word in "Bash" "Haskell" "Python"
do
  echo "Your language is $word".
done
\end{minted}

There is also a case instruction:
\begin{minted}{bash}
case $language in
  bash)
    echo "Bourne Again Shell!"
  ;;
  python|haskell)
    echo "Python or Haskell!"
    exit 1
  ;;
  *)
    echo "Unknown language!"
  ;; # optional
esac
\end{minted}

\subsubsection{Testing conditions}
Remember that \texttt{test} command follows symbolic links (except for the \texttt{-h} test).
\begin{compactenum}
\item \textbf{File tests}:
\begin{compactenum}
    \item \texttt{-e} file exists,
    \texttt{-s} file is nonempty,
    \item \texttt{-d} directory,
    \texttt{-f} regular file,
    \texttt{-h} symlink,
    \item \texttt{-b} block device,
    \texttt{-c} character device,
    \item \texttt{-p} named pipe,
    \texttt{-S} socket.
\end{compactenum}
\item \textbf{File permissions}:
\begin{compactenum}
    \item \texttt{-r} readable,
    \texttt{-w} writable,
    \texttt{-x} executable,
    \item \texttt{-u} setuid,
    \texttt{-g} setgid,
    \texttt{-k} sticky bit.
\end{compactenum}
\item \textbf{String tests}: \texttt{-z} empty, \texttt{-n} nonempty.
\item \textbf{Arithmetic tests}:
\begin{compactenum}
  \item \texttt{-eq} $=$,
  \texttt{-ne} $\neq$,
  \item \texttt{-lt} $<$,
  \texttt{-gt} $>$,
  \item \texttt{-le} $\le$,
  \texttt{-ge} $\ge$.
\end{compactenum}
\end{compactenum}

\subsubsection{Loops}
\begin{minted}{bash}
for var in "the first" "the second"; do
  echo "${var}"
done

for (( i = 1; i <= 10; i++ )); do
  echo "i = ${i}."
done # C-style

while read myline; do
  echo "It says ${myline}"
done < some_file
\end{minted}

As Bash Guide for Beginners by M. Garrels says:
\begin{compactenum}
\item the \texttt{break} statement is used to
exit the current loop before its normal ending.
\item the \texttt{continue} statement resumes iteration
of an enclosing while, until, select or for loop.
\end{compactenum}

\vfill\null
\columnbreak


% special files: /dev/null, /dev/zero, /proc/...

% special meaning of < > ; | * ? - one has to escape them
% ' '
% " "
