\documentclass[a4paper, twoside, 8pt]{extarticle}
\usepackage[
    left=1.2cm,
    right=1.2cm,
    top=2.25cm,
    bottom=1.25cm]{geometry}
\usepackage{multicol}

% extensive control of page headers and footers
\usepackage{fancyhdr} 
\makeatletter
\fancypagestyle{mypagestyle}
{\newpage \fancyfoot[C]{} \renewcommand{\footrulewidth}{0pt}}
\makeatother
\pagestyle{mypagestyle}
\headsep 5pt            

% highlighted source code
\usepackage{minted} 
\usemintedstyle{pastie}

% selects alternative section titles
\usepackage[compact]{titlesec} 
\titlespacing{\section}{0pt}{\parskip}{0}
\titlespacing{\subsection}{0pt}{\parskip}{0}
\titlespacing{\subsubsection}{0pt}{\parskip}{0}

% custom font
\usepackage{Alegreya}
% provides an extended symbol collection
\usepackage{amssymb} 
\usepackage{hyperref}
% reference last page
\usepackage{lastpage}
% layout with zero \parindent, non-zero \parskip 
\usepackage{parskip} 
% driver-independent color extensions
\usepackage{xcolor} 
% compact list environment
\usepackage{paralist}
\usepackage{microtype}

\newcommand{\manualbreak}{\vspace*{\fill}\columnbreak}

\newcommand{\cmdcore}{$\blacksquare$}
\newcommand{\cmdutil}{$\boxplus$}
\newcommand{\cmdvar}{$\square$}
 
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\begin{document}
\renewcommand{\footrulewidth}{0.4pt}
\fancyhead[LE,LO]{Linux/Bash -- quick reference (page \thepage/\pageref{LastPage})}
\fancyhead[RO,RE]{source: \url{https://git.io/vMQlp}} 
\fancyfoot[RF]{author: Remigiusz Suwalski,\\ date: \today}
\fancyfoot[LF]{\cmdcore \,: coreutils 8.27, \cmdutil \,: util-linux 2.29, \cmdvar \,: other commands.}

\begin{multicols*}{3}
\textbf{Bash}, a command line interface for interacting with the operating system, was created in the 1980s.
Other popular shells are \emph{zsh} and \emph{fish}.

\input{src/programming}

\input{src/shortcuts}

\input{src/style_guide}

\vfill\null\columnbreak

\input{src/sed_awk}

\input{src/regex}

\end{multicols*}

\newpage

\begin{multicols*}{3}
\section{Unix utilities and shell builtins}
% Based on https://en.wikipedia.org/wiki/Template:Unix_commands

\subsection{File system}
\input{src/unix_files}

\subsection{Processes}
\input{src/unix_processes}

\subsection{User environment}
\input{src/unix_user}

\subsection{Text processing}
\input{src/unix_text}

\subsection{Shell builtins}
\input{src/unix_builtins}

\subsection{Networking}
\input{src/unix_network}

\subsection{Searching}
\input{src/unix_search}

\subsection{Hardware}
\input{src/unix_hw}

\subsection{For programmers}
\input{src/unix_programmers}

\subsection{Miscellaneous}
\input{src/unix_miscellaneous}
\end{multicols*}
\end{document}

Todo:
\textbf{gp} invokes the PARI/GP calculator.
\textbf{pdflatex} runs the pdfTeX typesetter.

\textbf{apropos} searches the manual page names and descriptions.
\textbf{man} is an interface to the online reference manuals.

\textbf{ghci} is the Glasgow Haskell Compiler.
\textbf{ipython} is an interactive Python shell, see also
\textbf{python} and \textbf{python3}.
\textbf{gcc} is a C and C++ compiler.

nc - ?
